---
title: Making an animated ggplot
author: Cécile Sauder
date: '2018-10-14'
categories:
  - Data Visualization
tags:
  - gganimate
  - ggimage
  - ggplot2
  - magick
  - tidyverse
slug: making-an-animated-ggplot
---

I decide to talk about how I make my awesome blog banner in this first post. `r emo::ji("smile")`


# Why this banner ? 

It's a french word game with my family name Sauder => Saut d'R (R jump in english). That's why I decided to make a banner with the R-logo jumping on some (so cool) stickers. I choose stickers of packages that I use to do this animated ggplot. 

# Which packages ? 

```{r}
library(tidyverse)

#setRepositories(ind=1:2)
## install.packages("devtools")
#devtools::install_github("GuangchuangYu/ggimage")
library(ggimage)

library(magick)
#devtools::install_github('thomasp85/gganimate')
library(gganimate)
```

Firstly, I always use the **tidyverse** package, because it contains **dplyr**, **ggplot2**, **purrr**... and some others unavoidable packages. 

Then, to deal with images, my favorite package is [**magick**](https://ropensci.org/tutorials/magick_tutorial/), an other unavoidable package ! It allows to read/write/transform/convert images, and to make some beautiful GIF too. See the vignette for more informations, it's really cool.

To replace **ggplot2** points by some images, I find the [**ggimage**](https://cran.r-project.org/web/packages/ggimage/vignettes/ggimage.html) package. And to animate these images, the [**gganimated**](https://github.com/thomasp85/gganimate) package.

# Jumping trajectory

This part is not very interesting and you probably do this better, but it's just about describing jumps with data.

```{r}
x0 <- -8:8
y <- rep((-x0^2)/100 +1 ,3 )
y <- y + seq(0,3, length.out = length(y))
y <- c(y, rev(y))

#just to have a look
plot(y)
```

# Get images and tidy data

Firstly, a tibble (a tidy data.frame if you don't know yet) with the R trajectory `y`, the abscissa `x` and `x1` which will serve to animate R, and the R logo url directory in `image`.


```{r}

ly <- length(y)

#first tibble for R trajectory
d <- tibble(
x = 1:ly,
x1 = 1:ly,
y = y,
image = rep("https://www.r-project.org/logo/Rlogo.png",ly)
)
```

Then I decide to make a local copy of the R logo image, resizing it at 200px for witdh, because even if **ggimage** can deal with url images, it took a long time to do this with the `r ly` images. So I use the **magick** package to `read`, `scale`, and `write` the R logo. 


```{r}
#local copy of Rlogo
"https://www.r-project.org/logo/Rlogo.png" %>%
  image_read() %>%
  image_scale("200") %>%
  image_write("Rlogo.png")
```

I add the column `image2` to the tibble with the name of the R logo file.

```{r}
d <- d %>%
  mutate(image2 = rep("Rlogo.png",ly))

```


# Display and animate the R logo

Now we have all we need to animate the R logo. So let's test this !

Firstly just with `geom_image` :

```{r}
options(gganimate.dev_args = list(width = 400, height = 300))

gg <- ggplot(d, aes(x, y)) + 
  geom_image(aes(image=image2), size=.1 , by = 'width') 

gg
```
It seems to work, so now, let's animate this logo, after quiting lines and grey background with `theme_nothing`. For now, I test the "linear" ease but others are available and describe in the function `ease_aes` help. 
```{r, fig.height = 3, fig.width = 4}
gg <- gg +
  theme_nothing() +
  transition_time(x1) +
  ease_aes('linear')

gg
```


# Add the stickers on the plot

Now let's add the stickers. I make an other tibble to deal with a different `aes` in `ggplot`. I put the url directory of some beautiful stickers. 


```{r}
x3 = seq(0,ly, by = length(x0))
y3 = c(0.36,d$y[x3])
y3 = y3 - 0.4

d2 <- tibble(
x3 = x3+2,
y3 = y3,

hex = c(
"https://github.com/rstudio/hex-stickers/raw/master/PNG/blogdown.png",
"https://github.com/rstudio/hex-stickers/raw/master/PNG/devtools.png",
"https://github.com/rstudio/hex-stickers/raw/master/PNG/tibble.png",
"https://github.com/rstudio/hex-stickers/raw/master/PNG/pipe.png",
"https://github.com/thomasp85/gganimate/raw/master/man/figures/logo.png",
"https://github.com/rstudio/hex-stickers/raw/master/PNG/tidyverse.png",
"https://github.com/rstudio/hex-stickers/raw/master/PNG/ggplot2.png"
)
)
```

Now the part using **magick** to locally copy the images. To process all the images at once, I use the `map2_chr` function of the **purrr** package

```{r}
d2$hex %>%
  image_read() %>%
  image_scale("200") -> hex2

```

`hex2` il a tibble, so I transform it in a list to give it to `map2_chr`.
Why `map2_chr` and not just `map2` ? Because I want characters `r emo::ji("smile")`

You can do the same with `map2` if you `unlist` the result. 

```{r}
hex3 <- map2_chr(as.list(hex2), basename(d2$hex), image_write)

d2 <- d2 %>%
  mutate(hex3 = hex3)
```

Once the column with the files names added to the tibble, we can plot it. 
I just have to change `ylim` of the ggplot because `min(y3) < min(y)`

```{r, fig.height = 3, fig.width = 4}

gg <- gg + 
  ylim(min(y3)-0.2,max(y)) +
  geom_image(data = d2, aes(x=x3, y=y3, image = hex3), size = .1, by = 'height')

gg

```

Yes ! It's better like this. If you love the result you can save it with `anim_save`.

```{r}

#anim_save("saut_dR.gif")

```


##That's all for today `r emo::ji("kiss")`