---
title: Playgrounds in Montpellier
author: Cécile Sauder
date: '2019-07-04'
slug: playgrounds-in-montpellier
categories: []
tags:
  - map
  - Montpellier
description: ''
topics: []
header: "https://www.montpellier.fr/uploads/Image/cf/WEB_CHEMIN_14638_1329123196.jpg"
---

As a mom, I'm always looking for new playgrounds for Lexie, but when you look in google map I can't find them `r emo::ji("disappointed")`.

On the other hand, you can find in the open data of Montpellier several [datasets](http://data.montpellier3m.fr/datasets?query=aires%20de%20jeux%20Montpellier), I chose all those about the playgrounds of Montpellier. 

I find some useful help in this [post](https://dominicroye.github.io/en/2018/accessing-openstreetmap-data-with-r/) from Dominic Royé


```{r}
#install the osmdata, sf, tidyverse and ggmap package
if(!require("osmdata")) install.packages("osmdata")
if(!require("tidyverse")) install.packages("tidyverse")
if(!require("sf")) install.packages("sf")
if(!require("ggmap")) install.packages("ggmap")

#load packages
library(tidyverse)
library(osmdata)
library(sf)
library(ggmap)
library(leaflet)
```
If someone on ubuntu has the same error as me installing *sf* : ``` configure: error: gdal-config not found or not executable. ```, you can solve it typing in the terminal : 

```{bash}
sudo apt-get install gdal-bin proj-bin libgdal-dev libproj-dev
```

Of course, this is not solving the problem at first time, then I had an other error : ```configure: error: upgrade GDAL to 1.11.4 or later ``` so I wrote :

```{bash}
sudo add-apt-repository ppa:ubuntugis/ubuntugis-unstable

sudo apt-get update

sudo apt-get install libgdal-dev
```

And after that I was able to install *sf* !

Well, now let's see


```{r}
available_features()

available_tags("amenity")

available_tags("leisure")

#building the query
q <- getbb("Montpellier")%>%
      opq()%>%
       add_osm_feature("amenity", "kindergarten")

str(q) #query structure

playground <- osmdata_sf(q)
playground

```


Ok la suite



Ce que j'ai fait avant et qu'il faudrait ptet merger mais on verra 

```{r}
#our background map
mad_map <- get_map(getbb("Montpellier"),maptype = "toner-background")

#final map
ggmap(mad_map)+
  geom_sf(data=playground$osm_points,
          inherit.aes =FALSE,
          colour="#238443",
          fill="#004529",
          alpha=.5,
          size=4,
          shape=21)+
  labs(x="",y="")
```

Ok this is not too bad, but I can't zoom to see the street names. For that, there is the *leaflet* package.

```{r}

```


```{r}
playgrounds_by_type <- read_csv("http://data.montpellier3m.fr/sites/default/files/ressources/VilleMTP_MTP_JeuEnfantType.csv", 
                                locale = readr::locale(encoding = "latin1"))

playgrounds_by_age <- read_csv("http://data.montpellier3m.fr/sites/default/files/ressources/VilleMTP_MTP_JeuEnfantAge.csv", 
                               locale = readr::locale(encoding = "latin1"))

playgrounds_osm <- read_csv("http://data.montpellier3m.fr/sites/default/files/ressources/OSM_Metropole_aire_de_jeu.csv")
```

Note that to have correctly some french fuck*** character as **à** I had to add ``` locale = readr::locale(encoding = "latin1") ```. 


```{r}

```

