---
title: Analysis of Umbrella Academy's scripts
author: Cécile Sauder
date: '2019-02-23'
topics:
  - text mining
  - umbrella academy
  - series
tags:
  - tidytext
slug: umbrella-academy
header: "https://m.media-amazon.com/images/I/81pJBOc71wL._SS500_.jpg"
---

[The bible of text mining with R](https://www.tidytextmining.com/) (by Julia Silge and David Robinson) is very, very helpful !

I would like to see the evolution of the characters through the episodes but the scripts that I found no permit to do this because they don't precise who is speaking `r emo::ji("disappointed")`. 

Well, you have the scripts in a data frame, but not very tidy.



```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(tidytext)
```

# Words frequency

```{r}

df <- readRDS("df.RDS") %>%
  mutate(episode_number = str_sub(episodes_titles, 1, 1),
         episode_title = str_sub(episodes_titles, 4),
         script = str_remove_all(episodes_scripts, "\\[.*\\]")) %>%
  mutate(script = str_remove(script, "1")) %>%
  select(-episodes_scripts, -episodes_titles) 

df <- df %>%
  unnest_tokens(word, script, token = "words", to_lower = TRUE) %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE) %>%
  filter(n>20)

ggplot(df[1:25,], aes(reorder(word,n), n, fill = "skyblue")) + 
  geom_bar(stat = "identity") +
  #facet_wrap(~episode_number, nrow = 1) +
  


  geom_text(aes(label= as.character(n)), check_overlap = TRUE, size = 4) + 
  coord_flip() + 
  xlab(" ") 





```




Yes, that's all for today, tomorrow I'll analyze them, if `r emo::ji("baby")` wants it `r emo::ji("grinning")`